\documentclass[11pt, twoside, BCOR=8mm, DIV=12]{scrartcl}
\usepackage[german,ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{eurosym}
\usepackage[hyphens]{url}

\usepackage[onehalfspacing]{setspace}

\usepackage{float}
\usepackage{listingsutf8}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{pgfplots}

\title{{\Large INFORMATION VISUALIZATION, WINTER TERM 2017/18} \\ Exercise 4 – InfoVis Project Milestone 2}

\begin{document}
\maketitle
\section*{Task 1: Projekt - Milestone 2}
\begin{enumerate}[label=\alph*)]
\item \textbf{Goals and time plan}\\
Which features shall the final system offer?
\begin{enumerate}[label=\arabic*)]
\item Automatic animations
\item Interaction
\end{enumerate}
Which questions shall it be able to answer?
\begin{enumerate}[label=\arabic*)]
\item Does the number of visitors to the Oktoberfest influence the birth rate?
\item Does the number of tourists influence the number of Oktoberfest visitors?
\item Does the rising beer price influence the drinking behavior of Oktoberfest visitors?
\item Do other aspects (security risk) influence Oktoberfest visitors?
\item Does alcohol consumption of  Oktoberfest visitors influence the birth rate in Munich? How do alcohol consumption and birth rate in Munich in recent years?
\end{enumerate}
How do you plan to visualize the data?
\begin{enumerate}[label=\arabic*)]
\item HTML, JavaScript, D3.js
\item On a scrollable website
\item If a new visualization appears a small animation appears, too
\item Different diagramms like bar charts, liquid fill gauge
\end{enumerate}
Internal milestones to archieve the goals:
\begin{table}[H]
\begin{tabular}{l l}
Date & Goal \\
\hline
29.11.2017 & First visualizations of the individual data\\
\hline
13.12.2017 & Working prototype ready \\
\hline
28.12.2017 & First version ready, fine-tuning \\
\hline
11.01.2018 & Final version ready \\
\end{tabular}
\end{table}

\item Mockups
\item Documentation
\begin{itemize}
    \item large selection of visualizations: how to represent the data?
    \item http://infosthetics.com/ does not works on Wednesday, 29.11.2017
    \item Aha-Experiences: 
    \begin{itemize}
    	\item Generally: the conversion of the currency can not be recognized in the price trend (exchange rate $ 1,95583$\euro $* 0,511292 $)
        \item Hendel price has risen very high, especially in 2000
        \item before the conversion of the currency, the Hendel price has sometimes even fallen
    \end{itemize}
\end{itemize}
\end{enumerate}

Link to the presentation:\\
\url{https://docs.google.com/presentation/d/1xyitanyQwcztTYPRZUFfqwm49kiid7wTx3jvsXzBOEs/edit?usp=sharing}

\end{document}