\documentclass[11pt, twoside, BCOR=8mm, DIV=12]{scrartcl}
\usepackage[german,ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}

\usepackage[hyphens]{url}

\usepackage[onehalfspacing]{setspace}

%\usepackage{float}
\usepackage{listingsutf8}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{pgfplots}

\title{{\Large INFORMATIONSVISUALIZATION, WINTER TERM 2017/18} \\ Exercise 2 – InfoVis Project Milestone 1}

\begin{document}
\maketitle
\section*{Task 2: Project Draft and Project Plan}
\begin{enumerate}[label=\alph*)]
\item (technical/conceptual)challenges
\begin{enumerate}[label=\arabic*)]
\item first work with d3.js
\item finding good combination of data
\item finding good balance between Tufte and Holmes
\item incorporate interaction options that have a high information effect
\item don't waste time and don't produce something boring
\end{enumerate}
\item We want to find out if or to what extent the Oktoberfest has an influence on the birth rate in Munich.
The visualization should be interesting and understandable.
The data should be well combined.
Based on the provided data we can visualize the following aspects:
\begin{enumerate}[label=\arabic*)]
\item Does the number of visitors to the Oktoberfest influence the birth rate?
\item Does the number of tourists influence the number of Oktoberfest visitors?
\item Does the rising beer price influence the drinking behavior of Oktoberfest visitors?
\item Do other aspects (security risk) influence Oktoberfest visitors?
\item Does alcohol consumption of  Oktoberfest visitors influence the birth rate in Munich? How do alcohol consumption and birth rate in Munich in recent years?
\end{enumerate}
\item We will present our first project darft during the presentation tomorrow.
\end{enumerate}
\end{document}